\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{geometry}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\begin{document}

\title{Authorization to Release Educational Records}
\author{}
\date{}
\maketitle

\section*{Family Educational Rights and Privacy Act of 1974 as Amended (FERPA)}

I, \underline{\hspace{3cm}} \hspace{0.3cm} (Name), hereby voluntarily authorize officials in the University of Houston - Main identified below to disclose personally identifiable information from my educational records. (Please check the box or boxes that apply):

\begin{itemize}
    \item \checkbox{} Office of the University Registrar
    \item \checkbox{} Scholarships and Financial Aid
    \item \checkbox{} Student Financial Services
    \item \checkbox{} Undergraduate Scholars @ UH (formally USD)
    \item \checkbox{} University Advancement
    \item \checkbox{} Dean of Students Office
    \item \checkbox{} Other (Please Specify): \underline{\hspace{3cm}}
\end{itemize}

\textbf{Specifically, I authorize the disclosure of the following information or category of information. (Please check the box or boxes that apply):}

\begin{itemize}
    \item \checkbox{} Academic Advising Profile/Information
    \item \checkbox{} Academic Records
    \item \checkbox{} All University Records
    \item \checkbox{} Billing/Financial Aid
    \item \checkbox{} Disciplinary
    \item \checkbox{} Grades/Transcripts
    \item \checkbox{} Housing
    \item \checkbox{} Photos
    \item \checkbox{} Scholarships and/or Honors
    \item \checkbox{} Other (Please Specify): \underline{\hspace{3cm}}
\end{itemize}

The information may be released to: \underline{\hspace{5cm}} for the purpose of informing:

\begin{itemize}
    \item \checkbox{} Family
    \item \checkbox{} Educational Institution
    \item \checkbox{} Honor or Award
    \item \checkbox{} Employer/Prospective Employer
    \item \checkbox{} Public or Media of Scholarship
    \item \checkbox{} Other (Please Specify): \underline{\hspace{3cm}}
\end{itemize}

Please provide a password to obtain information via the phone:
\underline{\hspace{3cm}}. The password should not contain more than ten (10) letters. You must provide the password to the individuals or agencies listed above. The University will not release information to the caller if the caller does not have the password. A new form must be completed to change your password.

\textbf{This is to attest that I am a student signing this form. I understand the information may be released orally or in the form of copies of written records, as preferred by the requester. This authorization will remain in effect from the date it is executed until revoked by me, in writing, and delivered to the Department(s) identified above.}

\begin{flushright}
\textbf{Signature:} \underline{\hspace{3cm}} \\
\textbf{PSID:} \underline{\hspace{3cm}} \\
\textbf{Date:} \underline{\hspace{3cm}} 
\end{flushright}

\end{document}
